The Hyperedge Event Model

### 2018-05-30 paper/ba-HEM/ba-sample.tex
revision including diagram, section 2 and new PPE plot

Data generated under the HEM consists of $D$ unique edges. A single edge, indexed by $d \in [D]$, is represented by the three components: the sender $a_d \in [A]$, an indicator vector of receivers $\boldsymbol{r}_d = \{u_{dr} \}_{r=1}^{A}$, and the timestamp $t_d \in (0, \infty)$. For simplicity, we assume that edges are ordered by time such that $t_d \leq t_{d+1}$. While the model can be applied for two types of hyperedges---edges with (1) one sender and one or more receivers, and (2) one or more senders and one receiver---in this section we define the HEM by describing a process according to which hyperedge events are generated in continuous time, specifically for those involving one sender and one or more receivers (i.e., multicast). As a part of the generating process, we draw candidate receivers and candidate timestamps for each sender, which are the auxiliary variables in the HEM that serve as candidate data. Finally, we generate the observable data from the candidate data by taking the sender who generated the minimum candidate timestamp as an observed sender, the corresponding receivers as observed receivers, and the observed time as the timestamp of previous edge plus the smallest time generated. We explain these steps in more detail below. For the latter type of hyperedges---one receiver and one or more senders, we treat $a_d$ to be an indicator vector of senders $\boldsymbol{a}_d = \{u_{dr} \}_{a=1}^{A}$ and $r_d$ to be the single receiver, and then follow the alternative generative process provided in Appendix A, which is analogous to the process used for multicasts.

>>>>

In this section we define the HEM by describing a process according to which hyperedge events are generated in continuous time. Data generated under the HEM consists of $D$ unique edges. A single edge, indexed by $d \in [D]$, is represented by the three components: the sender $a_d \in [A]$, an indicator vector of receivers $\boldsymbol{r}_d = \{u_{dr} \}_{r=1}^{A}$, and the timestamp $t_d \in (0, \infty)$. For simplicity, we assume that edges are ordered by time such that $t_d \leq t_{d+1}$. While the model can be applied for two types of hyperedges---edges with (1) one sender and one or more receivers, and (2) one or more senders and one receiver---here we only present the generative process for those involving one sender and one or more receivers (i.e., multicast). As a part of the generating process, we draw candidate receivers and candidate timestamps for each sender, which are the auxiliary variables in the HEM that serve as candidate data. Finally, we generate the observable data from the candidate data by taking the sender who generated the minimum candidate timestamp as an observed sender, the corresponding receivers as observed receivers, and the observed time as the timestamp of previous edge plus the smallest time generated. We explain these steps in more detail below. For the latter type of hyperedges---one receiver and one or more senders, we treat $a_d$ to be an indicator vector of senders $\boldsymbol{a}_d = \{u_{dr} \}_{a=1}^{A}$ and $r_d$ to be the single receiver, and then follow the alternative generative process provided in Appendix A, which is analogous to the process used for multicasts.
